---
title: "6_plotting-and-analysing the Bayesian models"
---

```{r}
library(dplyr)
library(tidybayes)
library(data.table)
library(modelr)
library(tidyverse)
library(ggplot2)
library(ggpubr)

source(file = "plot.settings.paper.R")
```

# Load chosen models
The model chosen (m11) is loaded along with metadata
```{r}
#load data 
metadata_replicates =  readRDS("similarityreplicates_bc_sor.RDS")

metadata_replicates = metadata_replicates %>% mutate(selection_group = substring(treatment, 1,2)) %>%
    mutate(disturbed = case_when(selection == "C" ~"no", 
                                    selection == "D" ~"yes")) %>% mutate(time = day - mean(day))

period1_bc = readRDS("models_period1_braycurtis_replicatedivergence_m11_20052020.RDS")
period1_sor = readRDS("models_period1_sorensen_replicatedivergence_m11_20052020.RDS")
period2_bc = readRDS("models_period2_braycurtis_replicatedivergence_m11_20052020.RDS")
period2_sor =readRDS("models_period2_sorensen_replicatedivergence_m11_20052020.RDS")

m_p1_b = period1_bc[[1]]$m11.1_nor 
m_p1_s = period1_sor[[1]]$m11.1_nor 
m_p2_b =  period2_bc[[1]]$m11.1_nor 
m_p2_s = period2_sor[[1]]$m11.1_nor 

rm(period1_bc, period1_sor, period2_bc, period2_sor)
```

# Bray Curtis
## Mean BC change in both periods 
average values at start and end of each period.
```{r mean rep bc sim}
mean.sim.rep = metadata_replicates.bc %>% filter(day %in% c(2,28,29,50)) %>% group_by(disturbed, day, selection_group) %>% 
  summarise(mean.sim = mean(value), sd.sim  = sd(value))

undist.p1 = (mean.sim.rep$mean.sim[2] - mean.sim.rep$mean.sim[1]) / mean.sim.rep$mean.sim[1]*100
undist.p2 = (mean.sim.rep$mean.sim[4] - mean.sim.rep$mean.sim[3]) / mean.sim.rep$mean.sim[3]*100
dist.p1 = (mean.sim.rep$mean.sim[6] - mean.sim.rep$mean.sim[5]) / mean.sim.rep$mean.sim[5]*100
dist.p2 = (mean.sim.rep$mean.sim[8] - mean.sim.rep$mean.sim[7]) / mean.sim.rep$mean.sim[7]*100

data.frame(undist.p1, undist.p2, dist.p1, dist.p2)
```

First we plot the raw data and model for the BC models
## model with raw data 
```{r}
metadata_replicates_p1_b = metadata_replicates %>% filter(day < 29) %>% filter(distance == "Bray-Curtis")
metadata_replicates_p2_b = metadata_replicates %>% filter(day > 28) %>% filter(distance == "Bray-Curtis")

model_p1_pred = metadata_replicates_p1_b %>%
  group_by(selection, nutrient,day) %>%
  modelr::data_grid(time = seq_range(time, n = 9)) %>%
  tidybayes::add_fitted_draws(m_p1_b, re_formula = NA) %>% mutate(Period = "Period_1")
model_p1_pred = tibble(model_p1_pred)

model_p2_pred = metadata_replicates_p2_b %>%
  group_by(selection, nutrient,day) %>%
  data_grid(time = seq_range(time, n = 9)) %>%
  add_fitted_draws(m_p2_b, re_formula = NA) %>% mutate(Period = "Period_2")

both_predictions = bind_rows(model_p1_pred, model_p2_pred)
both_predictions = tibble(both_predictions)

both_predictions_bc = both_predictions %>% 
  mutate(selection_group = case_when(day < 29 & selection == "C" ~"UD", 
                                    day < 29 & selection == "D" ~"DU", 
                                    day > 28 & selection == "C" ~"DU", 
                                    day > 28 & selection == "D" ~"UD")) %>% 
  mutate(regime = paste0(selection_group, nutrient)) %>%
  mutate(disturbed = case_when(selection == "C" ~"no", 
                               selection == "D" ~"yes")) %>% 
  mutate(distance = "Bray-Curtis")
 
metadata_replicates.bc = metadata_replicates %>% 
  mutate(selection_group = substring(comparison, 1,2)) %>% 
  mutate(regime = substring(comparison, 1,3)) %>% 
  filter(distance == "Bray-Curtis") %>% 
  mutate(selection_group = stringr::str_replace(selection_group, "C", "U"), 
         regime = stringr::str_replace(regime, "C", "U"), 
         comparison = stringr::str_replace(comparison, "C", "U")) %>% mutate(regime = factor(regime, levels = c("UDH", "UDL", "DUH", "DUL")))

# saveRDS(object = both_predictions_bc, file = "both_predictions_bc_replicate_divergence_no_randomeffect.RDS")
# saveRDS(object = metadata_replicates.bc, file = "metadata_replicates_bc_fixednames.RDS")
```

```{r}
both_predictions_bc = readRDS("both_predictions_bc_replicate_divergence_no_randomeffect.RDS")
metadata_replicates.bc = readRDS("metadata_replicates_bc_fixednames.RDS")

bc.rep.sim = both_predictions_bc %>% 
  ggplot(aes(x = day, y = value, color = disturbed)) +
  stat_lineribbon(aes(y = .value, group = Period)) +
  geom_point(data = metadata_replicates.bc, aes(shape = regime), color = "black", size = 2.5) +
  geom_point(data = metadata_replicates.bc, aes(color = disturbed, shape = regime), size = 2) +
  facet_grid(~selection_group) + 
  my.theme + 
  ylab("Bray-Curtis replicate similarity divercence") + 
  scale_color_manual("Periodically disturbed", values = dist.col) + 
  scale_fill_manual("Confidence interval" ,values = alpha(c("grey86", "grey76", "grey50"),0.5)) + 
  scale_shape_manual("Regime", values = my.selection.shapes[c(2,1,4,3)]) + 
  geom_vline(xintercept = 28.5) +
  theme(legend.key.size = unit(0.3, "cm"), 
        axis.title.y = element_text(size = 8)) + 
  coord_cartesian(ylim = c(0,1), expand = FALSE,  xlim = c(1,51)) 
```

## Sigma estimation
```{r}
bcmodels = list(m_p1_b,m_p2_b)
sigma_rates = data.frame()

for (i in 1:2) {
  m = bcmodels[[i]]
  post = brms::posterior_samples(m)
  sigma_rate_model =  post %>% dplyr::transmute(C = b_sigma_time, 
                                                D = b_sigma_time + `b_sigma_time:selectionD`) %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Bray_Curtis") 
  colnames(sigma_rate_model) = c("selection","sigma_rate","Period" ,"model" )
  sigma_rates = bind_rows(sigma_rates, sigma_rate_model)
}

sigma_rates = sigma_rates %>% mutate(disturbed = case_when(selection == "C" ~"no", 
                                    selection == "D" ~"yes"), 
                                    
                                    peri.dis = paste0(disturbed, " P", substring(Period, 8)))

#saveRDS(object = sigma_rates, file = "simga_rates_BC.RDS")
```

```{r}
sigma_rates = readRDS(file = "simga_rates_BC.RDS")

sigma  = sigma_rates %>% 
ggplot(aes(x = sigma_rate, fill = disturbed, group = disturbed, y = disturbed)) +  
  my.theme + 
  facet_grid(~Period) + 
  stat_slab(color = "black", size = 0.4, alpha = 0.9) + 
  scale_fill_manual("Periodically disturbed", values = dist.col) + 
  xlab(expression(paste(Delta, sigma ,"/day"))) + 
  geom_vline(xintercept = 0) + 
  coord_cartesian(expand = FALSE)  +
  theme(axis.ticks.y = element_blank(), legend.position = "bottom") + 
    guides(fill = guide_legend(ncol = 1)) + 
    scale_x_continuous(breaks = c( -0.05, 0.05))

```

## replicate divergence change per day
```{r time rate calc bc}
bcmodels = list(m_p1_b,m_p2_b)

time_rates = data.frame()
for (i in 1:2) {
  m = bcmodels[[i]]
  post = posterior_samples(m)
  if (i == 1) {
  time_rate_model =  post %>% dplyr::transmute(CDH = b_time, 
                                               CDL = b_time + `b_time:nutrientL`,  
                                               DCH = b_time + `b_time:selectionD`, 
                                               DCL = b_time + `b_time:selectionD` + 
                                                 `b_time:nutrientL` + `b_time:selectionD:nutrientL`) %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Bray_Curtis", 
                           selection = substring(key, 1,1), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))
  
  colnames(time_rate_model)[1:2] =c("regime" ,   "time_rate")
  time_rates = bind_rows(time_rates, time_rate_model)
  }
else{
    time_rate_model =  post %>% dplyr::transmute(DCH = b_time, 
                                               DCL = b_time + `b_time:nutrientL`, 
                                               CDH = b_time + `b_time:selectionD`, 
                                               CDL = b_time + `b_time:selectionD` + `b_time:nutrientL` + `b_time:selectionD:nutrientL`) %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Bray_Curtis", 
                           selection = substring(key, 2,2), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))
    
    colnames(time_rate_model)[1:2] =c("regime" ,   "time_rate" )
    time_rates = bind_rows(time_rates, time_rate_model)
    
}
}

#saveRDS(object = time_rates, file = "rep_div_change_BC.RDS")
```

```{r}
time_rates = readRDS(file = "rep_div_change_BC.RDS")

time = time_rates %>% 
  ggplot(aes(x = time_rate, fill = reg, group = reg, y = disturbed)) +  
  my.theme + 
  facet_grid(~Period) + 
  stat_slab(color = "black",  size = 0.4, alpha = 0.9) + 
  scale_fill_manual("Periodically disturbed", values = a) + 
  xlab(expression(paste(Delta, "replicate similarity/day"))) +  
  geom_vline(xintercept = 0) + 
  coord_cartesian(expand = FALSE)  +
  theme(#axis.title.y = element_blank(), 
        #axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), legend.position = "bottom") + 
    guides(fill = guide_legend(ncol = 1)) + 
  scale_x_continuous(breaks = c(-0.02, 0, 0.02))

```

## combined plot 
```{r composite figure bc}

ggarrange(
  bc.rep.sim, 
  ggarrange(time, sigma, labels = c("b", "c"), legend = "none"), 
  ncol = 1, labels = c("a"), common.legend = TRUE, legend = "right", 
  heights = c(1.5,1) )
```

## sigma and time rate plot

We can categorise each draw of the model as either selection, drift or unclassified based on the similarity and sigma change per day. 
```{r}
bcmodels = list(m_p1_b,m_p2_b)
quant = data.frame()
for (i in 1:2) {
m = bcmodels[[i]]
post = posterior_samples(m)
 if (i == 1) { 
   time_reg =post %>% dplyr::transmute(CDH_time = b_time, 
                          CDL_time = b_time + `b_time:nutrientL`,  
                          DCH_time = b_time + `b_time:selectionD`, 
                          DCL_time = b_time + `b_time:selectionD` + `b_time:nutrientL` + `b_time:selectionD:nutrientL`) %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), 
                           model = "Bray_Curtis", 
                           selection = substring(key, 1,1), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))

sig_reg = post %>% dplyr::transmute(
                          CDH_sig = b_sigma_time, 
                          CDL_sig = b_sigma_time,
                          DCH_sig =b_sigma_time + `b_sigma_time:selectionD`, 
                          DCL_sg = b_sigma_time + `b_sigma_time:selectionD`)  %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Bray_Curtis", 
                           selection = substring(key, 1,1), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))

colnames(time_reg)[2] = "sim_change"
colnames(sig_reg)[2] = "sigma_change"
time_reg$key = seq(1, nrow(time_reg), 1)
sig_reg$key = seq(1, nrow(sig_reg), 1)

both_p1 = merge.data.frame(time_reg, sig_reg)
 } else {
   
   time_reg =post %>% dplyr::transmute(DCH_time = b_time, 
                          DCL_time = b_time + `b_time:nutrientL`,  
                          CDH_time = b_time + `b_time:selectionD`, 
                          CDL_time = b_time + `b_time:selectionD` + `b_time:nutrientL` + `b_time:selectionD:nutrientL`)  %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Bray_Curtis", 
                           selection = substring(key, 2,2), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))

sig_reg = post %>% dplyr::transmute(
                          DCH_sig = b_sigma_time, 
                          DCL_sig = b_sigma_time,
                          CDH_sig =b_sigma_time + `b_sigma_time:selectionD`, 
                          CDL_sg = b_sigma_time + `b_sigma_time:selectionD`)  %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Bray_Curtis", 
                           selection = substring(key, 2,2), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))

colnames(time_reg)[2] = "sim_change"
colnames(sig_reg)[2] = "sigma_change"
time_reg$key = seq(1, nrow(time_reg), 1)
sig_reg$key = seq(1, nrow(sig_reg), 1)

both_p2 = merge.data.frame(time_reg, sig_reg)
 }}

processes = bind_rows(both_p1, both_p2)
processes_quant = processes %>%
  mutate(process = case_when( (sim_change >= 0 & sigma_change <= 0) ~ "selection", 
                                          (sim_change < 0 & sigma_change > 0) ~ "drift", 
                              TRUE ~ "mix"))

#write.csv(x = processes_quant, file = "drift_sel_perdraw.csv")
```

```{r}
processes_quant = read.csv("drift_sel_perdraw.csv")

sigma = processes_quant %>% group_by(model, selection, peri.dis, Period) %>% 
  median_qi(sigma = sigma_change, .width = 0.95) 

similarity = processes_quant %>% group_by(model, selection, peri.dis, Period) %>% 
  median_qi(similarity = sim_change, .width = 0.95)

means_95_quantile = dplyr::left_join(similarity, sigma, by = c("model", "selection", "peri.dis", "Period"))
```

```{r}
bc_quantile = means_95_quantile %>% mutate(dis  = substr(peri.dis, 1,3)) %>%
  mutate(similarity = similarity*100, sigma = sigma*100, .lower.x = .lower.x*100, .upper.x = .upper.x*100, .lower.y = .lower.y*100, .upper.y = .upper.y*100) %>%
  ggplot2::ggplot(aes(x = similarity, y = sigma, 
                      fill = dis, color = dis, shape = Period)) + 
  #drift
  geom_rect(aes(xmin= 0,xmax = -10, ymin = 0, ymax = 10), 
            fill = "#009e73", alpha = 0.051, color = "transparent") + 
  #selection
  geom_rect(aes(xmin= 0,xmax = 10, ymin = 0, ymax = -10), 
            fill = "#cc79a7", alpha = 0.051, color = "transparent") + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin = .lower.y, ymax =.upper.y  ), size = 1) + 
  geom_errorbar(aes(xmin = .lower.x, xmax =.upper.x  ), size= 1) + 
  geom_point(size = 4,  color = "black") + 
  theme_bw() + 
  scale_shape_manual(values = c(21,22)) + 
  scale_fill_manual("Periodically disturbed", values = my.selection.values[c(1,3)])  + 
  scale_color_manual("Periodically disturbed",values = my.selection.values[c(1,3)]) + 
  guides(fill=guide_legend(nrow = 2, override.aes=list(shape=21, alpha = 1))) + 
    coord_cartesian(xlim = c(-2.5,2.5), ylim = c(-10,10), 
      expand = F) + 
   xlab(expression(paste(Delta, "replicate similarity % /day"))) + 
  ylab(expression(paste(Delta, sigma,"% /day"))) +
  facet_grid(~model)
```


## summarise rates 
```{r sigma means}
sigma_rates %>% group_by(disturbed, Period) %>% summarise(mean_rate = signif(mean(sigma_rate), 2), sd = signif(sd(sigma_rate), 2)) 

time_rates %>% group_by(disturbed, Period) %>% summarise(mean_rate = signif(mean(time_rate), 2), sd = signif(sd(time_rate), 2) ) 
```

# Sørensen 

## Mean Sør change in both periods 
```{r}
mean.sim.rep = metadata_replicates.sor %>% filter(day %in% c(2,28,29,50)) %>% group_by(disturbed, day, selection_group) %>% 
  summarise(mean.sim = mean(value), sd.sim  = sd(value))

undist.p1 = (mean.sim.rep$mean.sim[2] - mean.sim.rep$mean.sim[1]) / mean.sim.rep$mean.sim[1]*100
undist.p2 = (mean.sim.rep$mean.sim[4] - mean.sim.rep$mean.sim[3]) / mean.sim.rep$mean.sim[3]*100
dist.p1 = (mean.sim.rep$mean.sim[6] - mean.sim.rep$mean.sim[5]) / mean.sim.rep$mean.sim[5]*100
dist.p2 = (mean.sim.rep$mean.sim[8] - mean.sim.rep$mean.sim[7]) / mean.sim.rep$mean.sim[7]*100

data.frame(undist.p1, undist.p2, dist.p1, dist.p2)
```


## model with raw data 
```{r}
metadata_replicates_p1_s = metadata_replicates %>% filter(day < 29) %>% filter(distance == "Sørensen")
metadata_replicates_p2_s = metadata_replicates %>% filter(day > 28) %>% filter(distance == "Sørensen")

model_p1_pred = metadata_replicates_p1_s %>%
  group_by(selection, nutrient,day) %>%
  modelr::data_grid(time = seq_range(time, n = 9)) %>%
  tidybayes::add_fitted_draws(m_p1_s, re_formula = NA) %>% mutate(Period = "Period_1")
model_p1_pred = tibble(model_p1_pred)

model_p2_pred = metadata_replicates_p2_s %>%
  group_by(selection, nutrient,day) %>%
  data_grid(time = seq_range(time, n = 9)) %>%
  add_fitted_draws(m_p2_s, re_formula = NA) %>% mutate(Period = "Period_2")

both_predictions = bind_rows(model_p1_pred, model_p2_pred)
both_predictions = tibble(both_predictions)

both_predictions_sor = both_predictions %>% 
  mutate(selection_group = case_when(day < 29 & selection == "C" ~"UD", 
                                    day < 29 & selection == "D" ~"DU", 
                                    day > 28 & selection == "C" ~"DU", 
                                    day > 28 & selection == "D" ~"UD")) %>% 
  mutate(regime = paste0(selection_group, nutrient)) %>%
  mutate(disturbed = case_when(selection == "C" ~"no", 
                               selection == "D" ~"yes")) %>% 
  mutate(distance = "Sørensen")
 
metadata_replicates.sor = metadata_replicates %>% 
  mutate(selection_group = substring(comparison, 1,2)) %>% 
  mutate(regime = substring(comparison, 1,3)) %>% 
  filter(distance == "Sørensen") %>% 
  mutate(selection_group = stringr::str_replace(selection_group, "C", "U"), 
         regime = stringr::str_replace(regime, "C", "U"), 
         comparison = stringr::str_replace(comparison, "C", "U")) %>% mutate(regime = factor(regime, levels = c("UDH", "UDL", "DUH", "DUL")))

#saveRDS(object = both_predictions_sor, file = #"both_predictions_sor_replicate_divergence_no_randomeffect.RDS")
# saveRDS(object = metadata_replicates.sor, file = "metadata_replicates_sor_fixednames.RDS")
```

```{r}
both_predictions_sor = readRDS("both_predictions_sor_replicate_divergence_no_randomeffect.RDS")
metadata_replicates.sor = readRDS("metadata_replicates_sor_fixednames.RDS")

sor.rep.sim = both_predictions_sor %>% 
  ggplot(aes(x = day, y = value, color = disturbed)) +
  stat_lineribbon(aes(y = .value, group = Period)) +
  geom_point(data = metadata_replicates.sor, aes(shape = regime), color = "black", size = 2.5) +
  geom_point(data = metadata_replicates.sor, aes(color = disturbed, shape = regime), size = 2) +
  facet_grid(~selection_group) + 
  my.theme + 
  ylab("Sørensen replicate similarity divercence") + 
  scale_color_manual("Periodically disturbed", values = dist.col) + 
  scale_fill_manual("Confidence interval" ,values = alpha(c("grey86", "grey76", "grey50"),0.5)) + 
  scale_shape_manual("Regime", values = my.selection.shapes[c(2,1,4,3)]) + 
  geom_vline(xintercept = 28.5) +
  theme(legend.key.size = unit(0.3, "cm"), 
        axis.title.y = element_text(size = 8)) + 
  coord_cartesian(ylim = c(0.2,0.9), expand = FALSE,  xlim = c(1,51)) 
```


## Sigma estimation

```{r}
sormod = list(m_p1_s,m_p2_s)
sigma_rates = data.frame()
for (i in 1:2) {
  m = sormod[[i]]
  post = brms::posterior_samples(m)
  sigma_rate_model =  post %>% dplyr::transmute(C = b_sigma_time, 
                                                D = b_sigma_time + `b_sigma_time:selectionD`) %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Sørensen") 
  colnames(sigma_rate_model) = c("selection","sigma_rate","Period" ,"model" )
  sigma_rates = bind_rows(sigma_rates, sigma_rate_model)
}

sigma_rates = sigma_rates %>% mutate(disturbed = case_when(selection == "C" ~"no", 
                                    selection == "D" ~"yes"), 
                                    
                                    peri.dis = paste0(disturbed, " P", substring(Period, 8)))

#saveRDS(object = sigma_rates, file = "simga_rates_sor.RDS")
```

```{r}
sigma_rates = readRDS(file = "simga_rates_sor.RDS")

sigma_sor = sigma_rates %>% 
ggplot(aes(x = sigma_rate, fill = disturbed, group = disturbed, y = disturbed)) +  
  my.theme + 
  facet_grid(~Period) + 
  stat_slab(color = "black", size = 0.4, alpha = 0.9) + 
  scale_fill_manual("Periodically disturbed", values = dist.col) + 
  xlab(expression(paste(Delta, sigma ,"/day"))) + 
  geom_vline(xintercept = 0) + 
  coord_cartesian(expand = FALSE)  +
  theme(axis.ticks.y = element_blank(), legend.position = "bottom") + 
    guides(fill = guide_legend(ncol = 1)) + 
    scale_x_continuous(breaks = c( -0.05, 0.05))
```

## replicate divergence change per day
```{r }
sormod = list(m_p1_s,m_p2_s)

time_rates = data.frame()
for (i in 1:2) {
  m = sormod[[i]]
  post = posterior_samples(m)
  if (i == 1) {
  time_rate_model =  post %>% dplyr::transmute(CDH = b_time, 
                                               CDL = b_time + `b_time:nutrientL`,  
                                               DCH = b_time + `b_time:selectionD`, 
                                               DCL = b_time + `b_time:selectionD` + 
                                                 `b_time:nutrientL` + `b_time:selectionD:nutrientL`) %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Sørensen", 
                           selection = substring(key, 1,1), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))
  
  colnames(time_rate_model)[1:2] =c("regime" ,   "time_rate")
  time_rates = bind_rows(time_rates, time_rate_model)
  }
else{
    time_rate_model =  post %>% dplyr::transmute(DCH = b_time, 
                                               DCL = b_time + `b_time:nutrientL`, 
                                               CDH = b_time + `b_time:selectionD`, 
                                               CDL = b_time + `b_time:selectionD` + `b_time:nutrientL` + `b_time:selectionD:nutrientL`) %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Sørensen", 
                           selection = substring(key, 2,2), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))
    
    colnames(time_rate_model)[1:2] =c("regime" ,   "time_rate" )
    time_rates = bind_rows(time_rates, time_rate_model)
    
}
}

#saveRDS(object = time_rates, file = "rep_div_change_sorensen.RDS")
```

```{r}
time_rates = readRDS(file = "rep_div_change_sorensen.RDS")

time_sor = time_rates %>% 
  ggplot(aes(x = time_rate, fill = reg, group = reg, y = disturbed)) +  
  my.theme + 
  facet_grid(~Period) + 
  stat_slab(color = "black",  size = 0.4, alpha = 0.9) + 
  scale_fill_manual("Periodically disturbed", values = a) + 
  xlab(expression(paste(Delta, "replicate similarity/day"))) +  
  geom_vline(xintercept = 0) + 
  coord_cartesian(expand = FALSE)  +
  theme(axis.ticks.y = element_blank(), legend.position = "bottom") + 
    guides(fill = guide_legend(ncol = 1)) +
  scale_x_continuous(breaks = c(-0.005, 0.005))
```

## combined plot 
```{r }
ggarrange(
  sor.rep.sim, 
  ggarrange(time_sor, sigma_sor , labels = c("b", "c"), legend = "none"), 
  ncol = 1, labels = c("a"), common.legend = TRUE, legend = "right", 
  heights = c(1.5,1)
)
```

## sigma and time rate 
```{r}
sormod = list(m_p1_s,m_p2_s)
quant = data.frame()
for (i in 1:2) {
m = sormod[[i]]
post = posterior_samples(m)
 if (i == 1) { 
   time_reg =post %>% dplyr::transmute(CDH_time = b_time, 
                          CDL_time = b_time + `b_time:nutrientL`,  
                          DCH_time = b_time + `b_time:selectionD`, 
                          DCL_time = b_time + `b_time:selectionD` + `b_time:nutrientL` + `b_time:selectionD:nutrientL`) %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), 
                           model = "Sørensen", 
                           selection = substring(key, 1,1), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))

sig_reg = post %>% dplyr::transmute(
                          CDH_sig = b_sigma_time, 
                          CDL_sig = b_sigma_time,
                          DCH_sig =b_sigma_time + `b_sigma_time:selectionD`, 
                          DCL_sg = b_sigma_time + `b_sigma_time:selectionD`)  %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Sørensen", 
                           selection = substring(key, 1,1), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))

colnames(time_reg)[2] = "sim_change"
colnames(sig_reg)[2] = "sigma_change"
time_reg$key = seq(1, nrow(time_reg), 1)
sig_reg$key = seq(1, nrow(sig_reg), 1)

both_p1 = merge.data.frame(time_reg, sig_reg)
 } else {
   
   time_reg =post %>% dplyr::transmute(DCH_time = b_time, 
                          DCL_time = b_time + `b_time:nutrientL`,  
                          CDH_time = b_time + `b_time:selectionD`, 
                          CDL_time = b_time + `b_time:selectionD` + `b_time:nutrientL` + `b_time:selectionD:nutrientL`)  %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Sørensen", 
                           selection = substring(key, 2,2), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))

sig_reg = post %>% dplyr::transmute(
                          DCH_sig = b_sigma_time, 
                          DCL_sig = b_sigma_time,
                          CDH_sig =b_sigma_time + `b_sigma_time:selectionD`, 
                          CDL_sg = b_sigma_time + `b_sigma_time:selectionD`)  %>% 
  gather(key, value) %>% 
  group_by(key) %>% mutate(Period = paste0("Period_",i), model = "Sørensen", 
                           selection = substring(key, 2,2), 
                           disturbed = case_when(selection == "C" ~"no", 
                                                 selection == "D" ~"yes"), 
                           peri.dis = paste0(disturbed, " P", substring(Period, 8)), 
                           cc = substring(key, 3,3), 
                           reg = paste0(disturbed, "-", cc))

colnames(time_reg)[2] = "sim_change"
colnames(sig_reg)[2] = "sigma_change"
time_reg$key = seq(1, nrow(time_reg), 1)
sig_reg$key = seq(1, nrow(sig_reg), 1)

both_p2 = merge.data.frame(time_reg, sig_reg)
 }}

processes = bind_rows(both_p1, both_p2)
processes_quant = processes %>%
  mutate(process = case_when( (sim_change >= 0 & sigma_change <= 0) ~ "selection", 
                                          (sim_change < 0 & sigma_change > 0) ~ "drift", 
                              TRUE ~ "mix"))

#write.csv(x = processes_quant, file = "drift_sel_perdraw_sørensen.csv")
```

```{r}
processes_quant = read.csv("drift_sel_perdraw_sørensen.csv")

sigma = processes_quant %>% group_by(model, selection, peri.dis, Period) %>% 
  median_qi(sigma = sigma_change, .width = 0.95) 

similarity = processes_quant %>% group_by(model, selection, peri.dis, Period) %>% 
  median_qi(similarity = sim_change, .width = 0.95)

means_95_quantile = dplyr::left_join(similarity, sigma, by = c("model", "selection", "peri.dis", "Period"))
```

only means and 95% conf interval
```{r}
sorensen_quantile = means_95_quantile %>% mutate(dis  = substr(peri.dis, 1,3)) %>%
  mutate(similarity = similarity*100, sigma = sigma*100, .lower.x = .lower.x*100, .upper.x = .upper.x*100, .lower.y = .lower.y*100, .upper.y = .upper.y*100) %>%
  ggplot2::ggplot(aes(x = similarity, y = sigma, 
                      fill = dis, color = dis, shape = Period)) + 
  #drift
  geom_rect(aes(xmin= 0,xmax = -10, ymin = 0, ymax = 10), 
            fill = "#009e73", alpha = 0.051, color = "transparent") + 
  #selection
  geom_rect(aes(xmin= 0,xmax = 10, ymin = 0, ymax = -10), 
            fill = "#cc79a7", alpha = 0.051, color = "transparent") + 
  geom_vline(xintercept = 0) + 
  geom_hline(yintercept = 0) + 
  geom_errorbar(aes(ymin = .lower.y, ymax =.upper.y  ), size = 1) + 
  geom_errorbar(aes(xmin = .lower.x, xmax =.upper.x  ), size= 1) + 
  geom_point(size = 4,  color = "black") + 
  theme_bw() + 
  scale_shape_manual(values = c(21,22)) + 
  scale_fill_manual("Periodically disturbed", values = my.selection.values[c(1,3)])  + 
  scale_color_manual("Periodically disturbed",values = my.selection.values[c(1,3)]) + 
  guides(fill=guide_legend(nrow = 2, override.aes=list(shape=21, alpha = 1))) + 
    coord_cartesian(xlim = c(-1,1.2), ylim = c(-10,10), 
      expand = F) + 
   xlab(expression(paste(Delta, "replicate similarity % /day"))) + 
  ylab(expression(paste(Delta, sigma,"% /day"))) +
  facet_grid(~model)

```


## combined BC and Sorensen timerate sigma plot 
```{r}
ggarrange(bc_quantile, sorensen_quantile, common.legend = TRUE, legend = "right")
```

```{r sigma means}
sigma_rates %>% group_by(disturbed, Period) %>% summarise(mean_rate = signif(mean(sigma_rate), 2), sd = signif(sd(sigma_rate), 2)) 

time_rates %>% group_by(disturbed, Period) %>% summarise(mean_rate = signif(mean(time_rate), 2), sd = signif(sd(time_rate), 2) ) 
time_rates %>% group_by(disturbed, Period) %>% summarise(mean_rate = signif(mean(time_rate), 3), sd = signif(sd(time_rate), 2) ) 
```